N-dimensional Tic Tac Toe, an Adventure in Modules

### 2017-05-13 paper/paper.tex
minor fixes

\title{N-dimensional Tic Tac Toe, and Adventure in Modules}
\author{Alex Grasley \and Jeff Young \and Michael McGirr}
\date{}

@@

    end
  \end{verbatim}
  We decided against this approach i.e. isolating IO into a separate module,
  because it began to pollute our design's dependency graph with unwanted edges.
  In Haskell, type class instances exist in an global overloaded name space,
  that takes advantage of Haskell's dispatch system. So each data type that is
  implemented for the \texttt{Show} typeclass is able to be printed to StdOut
  \textit{without} carrying around its respective show function. This is not the
  case in SML, and it was sorely missed in our implementation. If we were to
  follow the Haskell style of IO (separating impure and pure code explicitly),
  then an IO dependency would be requisite anytime we needed to perform any IO.
  Thus, the IO node would become a dominating node in our dependency graph, and
  the its import into every functor would quickly become boilerplate and
  unwieldy. Hence, we chose an SML style design, where the structures that are
  mapped upon carry any relevant functions with them, which maintains a clean
  decomposition in SML. This type of structure bloat, although disgraceful to a
  Haskell programming, seems to be encouraged by SML's module system.

>>>>

\title{N-dimensional Tic Tac Toe, an Adventure in Modules}
\author{Alex Grasley \and Jeff Young \and Michael McGirr}
\date{}

@@

    end
  \end{verbatim}
  We decided against this approach i.e. isolating IO into a separate module,
  because it began to pollute our design's dependency graph with unwanted edges.
  In Haskell, type class instances exist in an global overloaded name space,
  that takes advantage of Haskell's dispatch system. So each data type that is
  implemented for the \texttt{Show} typeclass is able to be printed to StdOut
  \textit{without} carrying around its respective show function. This is not the
  case in SML, and it was sorely missed in our implementation. If we were to
  follow the Haskell style of IO (separating impure and pure code explicitly),
  then an IO dependency would be requisite anytime we needed to perform any IO.
  Thus, the IO node would become a dominating node in our dependency graph, and
  then its import into every functor would quickly become boilerplate and
  unwieldy. Hence, we chose an SML style design, where the structures that are
  mapped upon carry any relevant functions with them, which maintains a clean
  decomposition in SML. This type of structure bloat, although disgraceful to a
  Haskell programmer, seems to be encouraged by SML's module system, and is
  discussed in detail below.
